\textbf{\huge EHDA closed loop control system based on real time non-visual spray mode classification}\\ (Center, Bold, Times New Roman 14, maximum 15 words in english)

### 2023-01-18 Documentation/UFMG/Relatorio_3/Summary/Summary.tex
Documentation

\begin{figure}[H]
    \center
    \includegraphics[width=12cm]{images/images_folder_1/system_design.png}
    \caption{System Architecture}
\end{figure}

The algorithms implemented in the computer machine was developed in python by another student and it is already collecting data and classifying the spraying dynamics.
In Figure 3 and Figure 4 shows pictures took by the high speed camera of some of the possible spraying dynamics we can reach. The videos took by the camera is not being used in the classification
algorithm. It is used for manual validation of it.

\begin{multicols}{2}

    \begin{figure}[H]
        \center
        \includegraphics[width=5cm]{images/images_folder_3/conejetexample.png}
        \caption{cone jet mode}
    \end{figure}

    \begin{figure}[H]
        \center
        \includegraphics[width=5cm]{images/images_folder_3/multijetexample.png}
        \caption{multi jet mode}
    \end{figure}

\end{multicols}

>>>>

% \begin{figure}[H]
%     \center
%     \includegraphics[width=12cm]{images/images_folder_1/system_design.png}
%     \caption{System Architecture}
% \end{figure}

% The algorithms implemented in the computer machine was developed in python by another student and it is already collecting data and classifying the spraying dynamics.
% In Figure 3 and Figure 4 shows pictures took by the high speed camera of some of the possible spraying dynamics we can reach. The videos took by the camera is not being used in the classification
% algorithm. It is used for manual validation of it.

% \begin{multicols}{2}

%     \begin{figure}[H]
%         \center
%         \includegraphics[width=5cm]{images/images_folder_3/conejetexample.png}
%         \caption{cone jet mode}
%     \end{figure}

%     \begin{figure}[H]
%         \center
%         \includegraphics[width=5cm]{images/images_folder_3/multijetexample.png}
%         \caption{multi jet mode}
%     \end{figure}

% \end{multicols}

### 2023-01-18 Documentation/WT group/article1/main.tex
Documentation

\noindent\rule{15cm}{0.5pt}
	\begin{abstract}
		\textbf{Electrohydrodynamic Atomization (EHDA)} also known as Electrospray (ES), is a technology that uses a strong electric field (kV/cm) to manipulate liquid breakup into droplets. This technique allows the generation of droplets smaller than the nozzle diameter with a controlled droplet size, which means it can be used to produce uniformly sized particles in the micro/nanoscale range. This liquid spraying technique can generate different modes when both the liquid flow rate and the voltage vary with a narrow size dispersion. The most known mode is the cone-jet mode, because it can produce droplets in the micro and nanometric range with a narrow size dispersion.
		The article presents a novel closed-loop control system for electrohydraulic actuators (EHDA) that utilizes real-time, non-visual spray mode classification to improve performance and efficiency. The system utilizes current data from the experiment to classify the spray mode dynamics in real-time and adjust the EHDA parameters, such as pump flowrate and power supply voltage, to reach the desired spray mode and stabilize it. The proposed control algorithm is able to achieve improved accuracy and reduced waste compared to previous methods. The results of the system are discussed and its potential applications in industrial settings are highlighted.
		consists of objectives, methods, findings, and research contributions in 150 to 250 words which contains the main conclusions and provides important information and is accompanied by \textbf{5 keywords}. Furthermore, the determination of keywords needs to pay attention to important words contained in the title and abstract, separated by a semicolon. \textbf{The novelty} in this paper briefly explains why no one else has adequately researched the question. Then \textbf{the results} are made a list of the empirical findings and write the discussion in one or two sentences. \\ \\
		\let\thefootnote\relax\footnotetext{
			\small $^{*}$\textbf{Corresponding author.} \textit{
				\textit{E-mail address: \color{cyan}author4@email.com}}\\
			\color{black} Received: xx xxxxx 20xx,\quad
			Accepted: xx xxxxx 20xx and available online XX July 2022 \\
			\color{cyan} https://doi.org/10.1016/j.compeleceng.2021.107553

>>>>

\noindent\rule{15cm}{0.5pt}
	\begin{abstract}
		\textbf{Electrohydrodynamic Atomization (EHDA)} also known as Electrospray (ES), is a technology that uses a strong electric field (kV/cm) to manipulate liquid breakup into droplets. This technique allows the generation of droplets smaller than the nozzle diameter with a controlled droplet size, which means it can be used to produce uniformly sized particles in the micro/nanoscale range. This liquid spraying technique can generate different modes when both the liquid flow rate and the voltage vary with a narrow size dispersion. The most known mode is the cone-jet mode, because it can produce droplets in the micro and nanometric range with a narrow size dispersion.

		The article presents a novel closed-loop control system for electrohydraulic actuators (EHDA) that utilizes real-time, non-visual spray mode classification to improve performance and efficiency. The system utilizes current data from the experiment to classify the spray mode dynamics in real-time and adjust the EHDA parameters, such as pump flowrate and power supply voltage, to reach the desired spray mode and stabilize it. The proposed control algorithm is able to achieve improved accuracy and reduced waste compared to previous methods. The results of the system are discussed and its potential applications in industrial settings are highlighted.

		The beginning of EHDA researches started with Taylor. He noticed that using electric field in liquids small droplets could be created. That dynamics received his name as Taylor Cone jet.
		After that other scientists such as Willian Gilber, Prunet published about "Electric Modes". In the work of Sjaaks\cite{Sjaaks} he could classify the spraying dynamics using non-visual data. The data was
		being collected is the currrent data flowing throught the system. However, the automation of the experiment is not very well explored. This could bring better knowledge about the experiment since the variables are normally adjusted manually.
		This work is structured with the goal of .....

		consists of objectives, methods, findings, and research contributions in 150 to 250 words which contains the main conclusions and provides important information and is accompanied by \textbf{5 keywords}. Furthermore, the determination of keywords needs to pay attention to important words contained in the title and abstract, separated by a semicolon. \textbf{The novelty} in this paper briefly explains why no one else has adequately researched the question. Then \textbf{the results} are made a list of the empirical findings and write the discussion in one or two sentences. \\ \\
		\let\thefootnote\relax\footnotetext{
			\small $^{*}$\textbf{Corresponding author.} \textit{
				\textit{E-mail address: \color{cyan}author4@email.com}}\\
			\color{black} Received: xx xxxxx 20xx,\quad
			Accepted: xx xxxxx 20xx and available online XX July 2022 \\
			\color{cyan} https://doi.org/10.1016/j.compeleceng.2021.107553
